---
title: "Capstone Report"
author: "Fábio Franco Costa"
date: "November 4, 2015"
output: pdf_document
---
```{r,echo=FALSE}
load(file = './rdata/df_users.RData')
```

# Title
Do similar users rates places equally?

# Introduction
When you are using apps like YELP, you get ratings based on the average reviews from all users. In that situation I may get good ratings for a place that I would not really appreciate, because not every user are similar to others. My problem is testing if clusters of similar users rate places equally, so that I can use the average rate of this clusters to predict how I would rate some new place.

# Methods and Data
For our analysis, the first step was to decide a clustering strategy. We decided to use the features in the user database as our characteristics. We did some transformations and end up with the following structure:

```{r, echo=FALSE}
str(df_users)
```
We clustered the data using K means, for 15 clusters using the following command:
```{r, eval=FALSE}
cl_users <- kmeans(mtx_user, clusters_no,
                   iter.max = 1000, nstart = 5)
```
After that, we used Hypothesis Test to check if different groups have different average rates for the same business. We used a 90% confidence interval to our analysis because we didn't want to impose a very strict test.

# Results
We found that the

# Discussion
- Explain how you interpret the results of your analysis and what the implications are for your question/problem.
